Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2020-09-04 Scripts/Initial_Analysis.Rmd
Sent first draft to W. up to results

```{r fun_SummaryProp, eval = F, echo =F}
taxon_key <- 600006

@@

   eez_summary <- spp %>% 
     group_by(eez_name,eez_neighbour,time_step) %>% 
     summarise(
       n_spp = n(),
       min_eez = min(mean_spp, na.rm=T),
       max_eez = max(mean_spp, na.rm=T),
       sd_eez = sd(mean_spp, na.rm=T), # for some weird reason it wont work if the order is fliped
       mean_eez = mean(mean_spp,na.rm=T)
     ) %>% 
     select(eez_name:max_eez,mean_eez,sd_eez)

@@

   eez_summary <- spp %>% 
     group_by(eez_name,time_step) %>% 
     summarise(
       n_spp = n(),
       min_eez = min(mean_spp, na.rm=T),
       max_eez = max(mean_spp, na.rm=T),
       sd_eez = sd(mean_spp, na.rm=T), # for some weird reason it wont work if the order is fliped
       mean_eez = mean(mean_spp,na.rm=T)
     ) %>% 
     select(eez_name:max_eez,mean_eez,sd_eez)

@@

```{r fun_PropChange, eval = F, echo =F}
taxon_list <- unique(Transboundary_spp$taxon_key)[1:15]

@@

 proportion_change <- eez %>% 
   gather("variable","value",n_spp:sd_eez) %>% 
   spread(time_step,value) %>% 
   mutate_at(vars(
     "per_early" = early,
     "per_mid" = mid
     ),
            funs(round((((.-historical)/historical))*100,2))
   )

@@

@@

# --------------- #
# Load Proportion results
# --------------- #

# Read proportion results
# prop_results <- PropChange(Taxon_List_emer, links="y") %>% 
  # filter(!is.na(eez_neighbour)) %>% 
  # mutate(per_mid_plot =ifelse(per_mid >= 50, 50,
  #                          ifelse(per_mid <= -50,-50,per_mid)
  #                          ),
  #        per_early_plot =ifelse(per_early >= 50, 50,
  #                          ifelse(per_early <= -50,-50,per_early)
  #                          )
  #        )

@@

World_map <- rnaturalearth::ne_countries(scale = 'small', returnclass = c("sf")) %>%
  clean_names() %>% 
  # st_transform(crs = "+proj=eck4") %>%
  st_transform(crs = 4326) %>% # 4326
  left_join(World_map_dat,
            by = "iso_a3")

@@

Prop_results %>% 
  filter(variable == "n_spp") %>% 
  group_by() %>% 
  summarise(
    median(early,na.rm=T),
    sd(early,na.rm=T)
  )

# Prepare data from results
Data <- Prop_results %>% 
  # get coords for sources
  left_join(Eez_centroid,
            by = "eez_name") %>%
  rename(source = eez_name,
         start_lon = longitude,
         start_lat = latitude,
         eez_name=eez_neighbour) %>% 
  # get coords for targets
  left_join(Eez_centroid,
            by = "eez_name") %>% 
  rename(target = eez_name,
         end_lon = longitude,
         end_lat = latitude) %>% 
  ungroup() %>% 
  # Plot miscs
  mutate(
    per_early = ifelse(is.na(per_early),0,per_early),
    per_mid = ifelse(is.na(per_mid),0,per_mid)
  ) %>% 
  drop_na() %>%
  filter(
    variable %in% c("mean_eez","n_spp")#,
    # source %in% c("Brazil","Argentina","Chile","Peru","Uruguay")
  )

@@

# Create data path for line connections
paths <- network_data_sf %>% 
  sf::st_set_geometry(NULL) %>% 
  unnest() %>% 
  mutate_at(vars(X,Y), round,2) %>% 
  gather("time_step","per_chng",per_early:per_mid) %>% 
  mutate(per_plot = ifelse(per_chng > 100,100,per_chng))

@@

n_taxa_data <- Prop_results %>% 
  filter(variable == "n_spp") %>% 
  rename(sf_eez_name = eez_name) %>% 
  left_join(Matching_names) %>% 
  group_by(sau_fishing_entity,fishing_entity_id) %>% 
  summarise(total_spp = mean(early,na.rm=T))

@@

gc()# clean ram

@@

Prop_map <- ggplot() +
  geom_sf(data = subset(n_taxa_map, sovereignt != "Antarctica"),
          aes(fill = total_spp),
          size = 0.1,col = "white") +
geom_sf(data = World_eez_sf, size = 0.1, fill = "white", col = "gray30") +
geom_point(data = subset(Map_data, time_step == time & per_plot < 0),
           aes(start_lon,
               start_lat,
               col = per_plot),
           size = 0.05,
           col = "gray80",
           shape = 20,
           stroke = 1.5) +
geom_path(data = subset(paths, time_step == time & per_plot > 0),
          aes(X,
              Y,
              group = interaction(line_id,subline_id),
              col = per_plot
          ),
          size = 0.3,
          lineend = "round",
          arrow = arrow(length = unit(0.008, "npc"),
                        ends = "first"),
          show.legend = NA) +
  my_ggtheme_m() +
scale_colour_viridis(
  name="Average Gain of Stock-Share Ratio (%)\nand Number of taxa (n)",
  limits = c(0,max(Map_data$per_plot)),
  breaks = seq(0,max(Map_data$per_plot),10)#,
  # option="magma",
  # direction = -1
) +
scale_fill_viridis(
  name="Average Gain of Stock-Share Ratio (%)\nand Number of taxa (n)",
  limits = c(0,max(Map_data$per_plot)),
  breaks = seq(0,max(Map_data$per_plot),10)#,
  # alpha = 0.8
  # option="magma",
  # direction = -1
) +
ggsave("./Figures/fig_sup_1.png",
       width = 12,
       height = 8,
       units = "in"
)

@@

Lat_am_eez <- World_eez_sf %>% 
  rename(sf_eez_name = eez_name) %>% 
  left_join(Matching_names) %>% 
  filter(
    # sau_fishing_entity %in% Lat_am_land$sau_fishing_entity,
         !str_detect(sf_eez_name,"Pacific"),
         !sf_eez_name %in% c("USA (East Coast)","Suriname","Guyana","French Guiana","Bermuda (UK)","Brazil","El Salvador")
         )

# Lat_am_eez %>% filter(str_detect(sf_eez_name,"Tri"))

@@

Lat_am_map <- ggplot() +
  geom_sf(data = Lat_am_eez, size = 0.1, fill = "white", col = "gray30") +
  geom_sf(data = subset(n_taxa_map, sovereignt != "Antarctica"),
          aes(fill = total_spp),
          size = 0.1,col = "white") +
  geom_point(data = subset(Lat_am_data, time_step == time & per_plot < 0 ),
             aes(start_lon,
                 start_lat,
                 col = per_plot),
             size = 1,
             col = "gray30",
             shape = 20,
             stroke = 1.5) +
  geom_path(data = subset(Lat_am_paths, time_step == time & per_plot > 0),
            aes(X, Y,
                group = interaction(line_id,subline_id),
                col = per_plot
            ),
            size = 1,
            arrow = arrow(length = unit(0.05, "npc"),
                          ends = "first"),
            show.legend = NA) +
  coord_sf(xlim = c(-100, -55),ylim = c(9, 30)) + 
  labs(x = "Lon", y = "Lat") +
  scale_x_continuous(breaks = seq(-100,60,10)) +
  scale_y_continuous(breaks = seq(10,30,5)) +
  # my_ggtheme_m() +
  theme(legend.position = "",
        panel.background = element_rect(fill = "white", color = "white"),
        panel.grid.major =  element_line(color = "white")
        ) +
  scale_colour_viridis(
    name="Average Gain of\nStock-Share Ratio (%)",
    limits = c(0,max(Lat_am_data$per_plot)),
    breaks = seq(0,max(Lat_am_data$per_plot),10),
    # option="magma",
    # direction = -1
  )+
  scale_fill_viridis(
    name="Average Gain of\nStock-Share Ratio (%)",
    limits = c(0,max(Lat_am_data$per_plot)),
    breaks = seq(0,max(Lat_am_data$per_plot),10),
    # option="magma",
    # direction = -1
  );Lat_am_map

@@

# Med plot
Med_map <- ggplot() +
  geom_sf(data = Med_eez, size = 0.5, fill = "white", col = "gray30") +
  geom_sf(data = subset(n_taxa_map, sovereignt != "Antarctica"),
          aes(fill = total_spp),
          size = 0.1,col = "white") +
  geom_point(data = subset(Med_data, time_step == time & per_plot < 0 ),
             aes(start_lon,
                 start_lat,
                 col = per_plot),
             size = 1,
             col = "gray30",
             shape = 20,
             stroke = 1.5) +
  geom_path(data = subset(Med_paths, time_step == time & per_plot > 0),
            aes(X, Y,
                group = interaction(line_id,subline_id),
                col = per_plot
            ),
            size = 1,
            arrow = arrow(length = unit(0.05, "npc"),
                          ends = "first"),
            show.legend = NA) +
  coord_sf(xlim = c(-3, 35),ylim = c(30, 45)) +
  labs(x = "Lon", y = "Lat") +
  scale_x_continuous(breaks = seq(-5,35,10)) +
  scale_y_continuous(breaks = seq(30,50,5)) +
  # my_ggtheme_m() +
  theme(legend.position = "",
        panel.background = element_rect(fill = "white", color = "white"),
        panel.grid.major =  element_line(color = "white")
        ) +
  scale_colour_viridis(
    name="Average Gain of\nStock-Share Ratio (%)",
    limits = c(0,max(Med_data$per_plot)),
    breaks = seq(0,max(Med_data$per_plot),5),
    # option="magma",
    # direction = -1
  )+
  scale_fill_viridis(
    name="Average Gain of\nStock-Share Ratio (%)",
    limits = c(0,max(Med_data$per_plot)),
    breaks = seq(0,max(Med_data$per_plot),5),
    # option="magma",
    # direction = -1
  );Med_map

@@

Eu_map <- ggplot() +
  geom_sf(data = Eu_eez, size = 0.5, fill = "white", col = "gray30") +
  geom_sf(data = subset(n_taxa_map, sovereignt != "Antarctica"),
          aes(fill = total_spp),
          size = 0.1,col = "white") +
  geom_point(data = subset(Med_data, time_step == time & per_plot < 0 ),
             aes(start_lon,
                 start_lat,
                 col = per_plot),
             size = 1,
             col = "gray30",
             shape = 20,
             stroke = 1.5) +
  geom_path(data = subset(Eu_paths, time_step == time & per_plot > 0),
            aes(X, Y,
                group = interaction(line_id,subline_id),
                col = per_plot
            ),
            size = 1,
            arrow = arrow(length = unit(0.05, "npc"),
                          ends = "first"),
            show.legend = NA) +
  coord_sf(xlim = c(-15, 30), ylim = c(45, 65)) +
  labs(x = "Lon", y = "Lat") +
  scale_y_continuous(breaks = seq(45,65,10)) +
  # scale_x_continuous(breaks = seq(45,65,10)) +
  # my_ggtheme_m() +
  theme(legend.position = "",
        panel.background = element_rect(fill = "white", color = "white"),
        panel.grid.major =  element_line(color = "white")
        ) +
  scale_colour_viridis(
    name="Average Gain of\nStock-Share Ratio (%)",
    limits = c(0,max(Eu_data$per_plot)),
    breaks = seq(0,max(Eu_data$per_plot),5),
    # option="magma",
    # direction = -1
   )+
  scale_fill_viridis(
    name="Average Gain of\nStock-Share Ratio (%)",
    limits = c(0,max(Med_data$per_plot)),
    breaks = seq(0,max(Med_data$per_plot),5),
    # option="magma",
    # direction = -1
  );Eu_map

## ------------------- ##
# Final Figure
## ------------------- ##

# gc()
# plot_all <- ggdraw() +
#       # map
#       draw_plot(Prop_map, x = 0, y = 0.45, width = 1, height = 0.58) +
#       # Lat America reg plor
#       draw_plot(Lat_am_map, x = 0.1, y = 0.08, width = 0.3, height = 0.4) +
#       # Europe reg plot
#       draw_plot(Eu_map, x = 0.35, y = 0.08, width = 0.3, height = 0.4) +
#       # Med regional plot
#       draw_plot(Med_map, x = 0.65, y = 0.08, width = 0.3, height = 0.4) +
#       draw_plot_label(label = c("a", "b"), 
#                       size = 20,
#                       x = c(0, 0), 
#                       y = c(1, 0.45)
#       ) #+
#       # draw_plot_label(label = c("Revenue (USD) | Catch (Tonnes)","(Million)"), 
#                       # size = 8,
#                       # x = c(0.325,0.485), 
#                       # y = c(0.31,0.29)
#       )
#     
#     
#     save_plot(
#       # paste(Figures_Path,"100_25_Bins_Value_Region.png",sep=""),
#       "test.png",
#       plot_all,
#       base_height = 8,
#       base_width = 8
#     )

@@

@@

Average_data <- Dem_pel %>% 
  group_by(un_sub_region) %>% 
  summarise(mean_toe = mean(emerging_yr,na.rm=T)) %>% 
  mutate(regional_average="average")

# Dem Pelagic boxplot
ggplot(Dem_pel) +
  geom_hline(data = Average_data,
             aes(
               yintercept = mean_toe,
               colour = regional_average
             ),
             linetype = "dashed"
             ) +
  geom_boxplot(
    aes(
      x = reorder_within(DemersPelag,emerging_yr,un_sub_region),
      y = emerging_yr,
      fill = DemersPelag
    ),
    alpha = 0.8
  ) +
  facet_wrap(~un_sub_region,scales = "free") +
  scale_fill_viridis("Habitat preference",
                     discrete = T) +
  scale_color_grey("Regional average") +
  xlab("") +
  ylab("Time of emergence") +
  my_ggtheme_p() +
  theme(
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    legend.position = "right"
  ) +
  scale_x_reordered() +
  ggsave("./Figures/regional_hab_boxplot.png",
         width = 14,
         height = 8,
         units = "in"
  )
```

>>>>

```{r fun_SummaryProp, eval = F, echo =F}

@@

    # Number of SSR stocks
    n_ssr <- spp %>% 
      group_by(eez_name,time_step) %>% 
      summarise(
        n_spp = length(unique(taxon_key))
      ) %>% 
      spread(time_step,n_spp) %>% 
      mutate_at(vars(early,mid),
                .funs = ~(./historical)*100
      ) %>% 
      select(-historical) %>%
      gather("time_step","n_per",early:mid)

    # Min, max and median change per eez_name and neighbour
    eez_summary <- spp %>% 
      group_by(eez_name,eez_neighbour,time_step) %>% 
      summarise(
        min_eez = min(mean_spp, na.rm=T),
        max_eez = max(mean_spp, na.rm=T),
        sd_eez = sd(mean_spp, na.rm=T), # for some weird reason it wont work if the order is fliped
        mean_eez = median(mean_spp,na.rm=T)
        ) %>% 
      select(eez_name:max_eez,mean_eez,sd_eez) %>% 
      left_join(n_ssr)

@@

    eez_summary <- spp %>% 
      group_by(eez_name,time_step) %>% 
      summarise(
        n_spp = length(unique(taxon_key)),
        # n_spp = n(),
        min_eez = min(mean_spp, na.rm=T),
        max_eez = max(mean_spp, na.rm=T),
        sd_eez = sd(mean_spp, na.rm=T), # for some weird reason it wont work if the order is fliped
        mean_eez = mean(mean_spp,na.rm=T)
        ) %>% 
      select(eez_name:max_eez,mean_eez,sd_eez)

@@

```{r fun_PropChange, eval = F, echo =F}

@@

  proportion_change <- eez %>% 
    gather("variable","value",min_eez:n_per) %>% 
    spread(time_step,value) %>% 
    mutate_at(vars(
      "per_early" = early,
      "per_mid" = mid
    ),
    funs(round((((.-historical)/historical))*100,2))
    )

@@

Neighbours_n <- Neighbours %>% 
  group_by(eez_name) %>% 
  summarise(
    n = length(unique(eez_neighbour))
  )

@@

# --------------- #
# Load Proportion results
# --------------- #
# Get taxon list
Taxon_list <- list.files(my_path("R",extra_path = "Proportion_2005"))

# clean names for function
Taxon_list <- gsub(".*_","",Taxon_list)

# clean names for function
Taxon_list <- gsub(".csv","",Taxon_list)

# Read proportion results
Prop_results <- PropChange(Taxon_list, links="y") %>%
  filter(!is.na(eez_neighbour)) %>%
  mutate(per_mid_plot =ifelse(per_mid >= 50, 50,
                              ifelse(per_mid <= -50,-50,per_mid)
  ),
  per_early_plot =ifelse(per_early >= 50, 50,
                         ifelse(per_early <= -50,-50,per_early)
  )
  )

@@

World_map <- rnaturalearth::ne_countries(scale = 'small', returnclass = c("sf")) %>%
  clean_names() %>% 
  select(iso_a3,sovereignt,sov_a3,name,name_long,region_wb,continent,geometry) %>% 
  # st_transform(crs = "+proj=eck4") %>%
  st_transform(crs = 4326) %>% # 4326
  mutate(iso_a3 = ifelse(sovereignt == "Norway","NOR",
                         ifelse(name == "France","FRA",
                                iso_a3)
                         )
         ) %>% 
    left_join(World_map_dat,
            by = "iso_a3")

@@

Prop_results %>% 
  filter(variable == "n_per") %>% 
  group_by() %>% 
  summarise(
    median(early,na.rm=T),
    sd(early,na.rm=T)
  )

# Prepare data from results
Data <- Prop_results %>% 
  # get coords for sources
  left_join(Eez_centroid,
            by = "eez_name") %>%
  rename(source = eez_name,
         start_lon = longitude,
         start_lat = latitude,
         eez_name=eez_neighbour) %>% 
  # get coords for targets
  left_join(Eez_centroid,
            by = "eez_name") %>% 
  rename(target = eez_name,
         end_lon = longitude,
         end_lat = latitude) %>% 
  ungroup() %>% 
  # Plot miscs
  mutate(
    per_early = ifelse(is.na(per_early),0,per_early),
    per_mid = ifelse(is.na(per_mid),0,per_mid)
  ) %>% 
  drop_na() %>%
  filter(
    variable %in% c("mean_eez","n_per")#,
    # source %in% c("Brazil","Argentina","Chile","Peru","Uruguay")
  )

@@

# Create data path for line connections
paths <- network_data_sf %>% 
  sf::st_set_geometry(NULL) %>% 
  unnest() %>% 
  mutate_at(vars(X,Y), round,2) %>% 
  gather("time_step","per_chng",per_early:per_mid) %>% 
  mutate(per_plot = ifelse(per_chng > 100,100,per_chng),
         direction = ifelse(per_chng > 0,"positive","negative")
         )

@@

n_taxa_data <- Prop_results %>% 
  filter(variable == "n_per") %>%
  select(eez_name,early,mid) %>% 
  rename(sf_eez_name = eez_name) %>% 
  left_join(Matching_names) %>% 
  group_by(sau_fishing_entity,fishing_entity_id) %>% 
  summarise(avrg_spp_per = mean(early,na.rm=T))

@@

mean(n_taxa_data$avrg_spp_per,na.rm=T)

# Rectangles dataset
# coord_sf(xlim = c(-3, 35),ylim = c(30, 45)) +
Rectangles <- tibble(
    x1=c(-100,-3,-14), #LatAm, Med, NE
    x2=c(-55,35,23),
    y1=c(9,31,50), 
    y2=c(30,44,67)
  )

# gc()# clean ram

@@

Prop_map <- ggplot() +
  geom_sf(data = subset(n_taxa_map, sovereignt != "Antarctica"),
          aes(fill = avrg_spp_per),
          size = 0.1,col = "white") +
  geom_sf(data = World_eez_sf, size = 0.1, fill = "white", col = "gray30") +
  geom_point(data = subset(Map_data, time_step == time & per_plot < 0),
             aes(start_lon,
                 start_lat
             ),
             size = 0.05,
             col = "gray80",
             shape = 20,
             stroke = 1.5) +
  geom_path(data = subset(paths, time_step == time & per_plot > 0),
            aes(X,
                Y,
                group = interaction(line_id,subline_id),
                col = per_plot
            ),
            size = 0.3,
            lineend = "round",
            arrow = arrow(length = unit(0.008, "npc"),
                          ends = "first"),
            show.legend = NA) +
  # Closeup Rectangles 
  geom_rect(data=Rectangles,
            aes(xmin=x1, 
                xmax=x2,
                ymin=y1,
                ymax=y2),
            color="grey50", 
            fill = NA,
            linetype = "dashed"
            ) +
  my_ggtheme_m() +
  scale_colour_viridis(
    name="Stock-Share Ratio Gain \nand taxa change (%)",
    limits = c(0,max(Map_data$per_plot)),
    breaks = seq(0,max(Map_data$per_plot),10)#,
    # option="magma",
    # direction = -1
  ) +
  scale_fill_viridis(
    name="Stock-Share Ratio Gain \nand taxa change (%)",
    limits = c(0,max(Map_data$per_plot)),
    breaks = seq(0,max(Map_data$per_plot),10)#,
    # alpha = 0.8
    # option="magma",
    # direction = -1
  ) #+
  # ggsave("./Figures/fig_sup_1.png",
  # width = 12,
  # height = 8,
  # units = "in"
  # )

@@

Lat_am_eez <- World_eez_sf %>% 
  rename(sf_eez_name = eez_name) %>% 
  left_join(Matching_names) %>% 
  filter(
         !str_detect(sf_eez_name,"Pacific"),
         !sf_eez_name %in% c("USA (East Coast)","Suriname","Guyana","French Guiana","Bermuda (UK)","Brazil","El Salvador")
         )

@@

Lat_am_map <- ggplot() +
  geom_sf(data = Lat_am_eez, size = 0.1, fill = "white", col = "gray30") +
  geom_sf(data = subset(n_taxa_map, sovereignt != "Antarctica"),
          aes(fill = avrg_spp_per),
          size = 0.1,col = "white") +
  geom_point(data = subset(Lat_am_data, time_step == time & per_plot < 0 ),
             aes(start_lon,
                 start_lat,
                 col = per_plot),
             size = 1,
             col = "gray30",
             shape = 20,
             stroke = 1.5) +
  geom_path(data = subset(Lat_am_paths, time_step == time & per_plot > 0),
            aes(X, Y,
                group = interaction(line_id,subline_id),
                col = per_plot
            ),
            size = 1,
            arrow = arrow(length = unit(0.05, "npc"),
                          ends = "first"),
            show.legend = NA) +
  coord_sf(xlim = c(-100, -55),ylim = c(9, 30)) + 
  labs(x = "", y = "") +
  scale_x_continuous(breaks = seq(-100,60,10)) +
  scale_y_continuous(breaks = seq(10,30,10)) +
  my_ggtheme_m() +
  theme(legend.position = "",
        panel.background = element_rect(fill = "white", color = "white"),
        panel.grid.major =  element_line(color = "white")
        ) +
  scale_colour_viridis(
    name="Average Gain of\nStock-Share Ratio (%)",
    limits = c(0,max(Lat_am_data$per_plot)),
    breaks = seq(0,max(Lat_am_data$per_plot),10),
    # option="magma",
    # direction = -1
  )+
  scale_fill_viridis(
    name="Average Gain of\nStock-Share Ratio (%)",
    limits = c(0,max(Lat_am_data$per_plot)),
    breaks = seq(0,max(Lat_am_data$per_plot),10),
    # option="magma",
    # direction = -1
  );Lat_am_map

@@

# Med plot
Med_map <- ggplot() +
  geom_sf(data = Med_eez, size = 0.5, fill = "white", col = "gray30") +
  geom_sf(data = subset(n_taxa_map, sovereignt != "Antarctica"),
          aes(fill = avrg_spp_per),
          size = 0.1,col = "white") +
  geom_point(data = subset(Med_data, time_step == time & per_plot < 0 ),
             aes(start_lon,
                 start_lat,
                 col = per_plot),
             size = 1,
             col = "gray30",
             shape = 20,
             stroke = 1.5) +
  geom_path(data = subset(Med_paths, time_step == time & per_plot > 0),
            aes(X, Y,
                group = interaction(line_id,subline_id),
                col = per_plot
            ),
            size = 1,
            arrow = arrow(length = unit(0.05, "npc"),
                          ends = "first"),
            show.legend = NA) +
  coord_sf(xlim = c(-3, 35),ylim = c(30, 45)) +
  labs(x = "", y = "") +
  scale_x_continuous(breaks = seq(-5,35,10)) +
  scale_y_continuous(breaks = seq(30,50,5)) +
  my_ggtheme_m() +
  theme(legend.position = "",
        panel.background = element_rect(fill = "white", color = "white"),
        panel.grid.major =  element_line(color = "white")
        ) +
  scale_colour_viridis(
    name="Average Gain of\nStock-Share Ratio (%)",
    limits = c(0,max(Med_data$per_plot)),
    breaks = seq(0,max(Med_data$per_plot),5),
    # option="magma",
    # direction = -1
  )+
  scale_fill_viridis(
    name="Average Gain of\nStock-Share Ratio (%)",
    limits = c(0,max(Med_data$per_plot)),
    breaks = seq(0,max(Med_data$per_plot),5),
    # option="magma",
    # direction = -1
  )#;Med_map

@@

Eu_map <- ggplot() +
  geom_sf(data = Eu_eez, size = 0.5, fill = "white", col = "gray30") +
  geom_sf(data = subset(n_taxa_map, sovereignt != "Antarctica"),
          aes(fill = avrg_spp_per),
          size = 0.1,col = "white") +
  geom_point(data = subset(Med_data, time_step == time & per_plot < 0 ),
             aes(start_lon,
                 start_lat,
                 col = per_plot),
             size = 1,
             col = "gray30",
             shape = 20,
             stroke = 1.5) +
  geom_path(data = subset(Eu_paths, time_step == time & per_plot > 0),
            aes(X, Y,
                group = interaction(line_id,subline_id),
                col = per_plot
            ),
            size = 1,
            arrow = arrow(length = unit(0.05, "npc"),
                          ends = "first"),
            show.legend = NA) +
  coord_sf(xlim = c(-15, 30), ylim = c(45, 65)) +
  labs(x = "", y = "") +
  scale_y_continuous(breaks = seq(45,65,10)) +
  # scale_x_continuous(breaks = seq(45,65,5)) +
  my_ggtheme_m() +
  theme(legend.position = "",
        panel.background = element_rect(fill = "white", color = "white"),
        panel.grid.major =  element_line(color = "white")
        ) +
  scale_colour_viridis(
    name="Average Gain of\nStock-Share Ratio (%)",
    limits = c(0,max(Eu_data$per_plot)),
    breaks = seq(0,max(Eu_data$per_plot),5),
    # option="magma",
    # direction = -1
   )+
  scale_fill_viridis(
    name="Average Gain of\nStock-Share Ratio (%)",
    limits = c(0,max(Med_data$per_plot)),
    breaks = seq(0,max(Med_data$per_plot),5),
    # option="magma",
    # direction = -1
  )#;Eu_map

# Legend
map_plot <- get_legend(Prop_map)

Prop_map <- Prop_map + 
  theme(legend.position = "")

## ------------------- ##
# Render final plot
## ------------------- ##

# Clean memory
gc()

# Draw figure
plot_all <- ggdraw() +
  # Main map
  draw_plot(Prop_map, x = 0, y = 0.40, width = 1, height = 0.6) +
  # Latin America and the Car.
  draw_plot(Lat_am_map, x = 0.01, y = 0.02, width = 0.33, height = 0.45) +
  # Europe
  draw_plot(Eu_map, x = 0.33, y = 0.01, width = 0.33, height = 0.45) +
  # The Med
  draw_plot(Med_map, x = 0.66, y = 0.02 , width = 0.33, height = 0.45) +
  # Legend
  draw_plot(map_plot, x = 0.3, y = 0, width = 0.59, height = 0.1) +
  # Labels
  draw_plot_label(label = c("A", "B", "The Caribbean","North West Europe","The Mediterranean"),
                  size = c(20,20,15,15,15),
                  x = c(0.01,0.01,0.058,0.38,0.70),
                  y = c(1,0.45,0.44,0.44,0.44)
  )

# Save plot
save_plot(
  "./Figures/figS3.png",
  plot_all,
  base_height = 10,
  base_width = 12
)

@@

# Needs previous chunk

@@

Average_data <- Dem_pel %>% 
  group_by(un_sub_region) %>% 
  summarise(mean_toe = mean(emerging_yr,na.rm=T)) %>% 
  mutate(regional_average="regional average")

# Dem Pelagic boxplot
ggplot(Dem_pel) +
  geom_hline(data = Average_data,
             aes(
               yintercept = mean_toe,
               colour = regional_average
             ),
             linetype = "dashed"
             ) +
  geom_boxplot(
    aes(
      x = reorder_within(DemersPelag,emerging_yr,un_sub_region),
      y = emerging_yr,
      fill = DemersPelag
    ),
    alpha = 0.8
  ) +
  facet_wrap(~un_sub_region,scales = "free_x") +
  scale_fill_viridis("Habitat preference",
                     discrete = T) +
  scale_color_grey("") +
  xlab("") +
  ylab("Time of emergence") +
  my_ggtheme_p() +
  theme(
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    legend.position = "right"
  ) +
  scale_x_reordered() +
  ggsave("./Figures/regional_hab_boxplot.png",
         width = 14,
         height = 8,
         units = "in"
  )
```
